\documentclass[11pt,a4paper]{article}
\usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm, bindingoffset=0cm]{geometry}
\usepackage{palatino}
\usepackage{tabularx}
\usepackage{array}

\def\tbf{\textbf}
\def\ttt{\texttt}
\def\sml#1{\small{#1}\normalsize}
\def\lrg#1{\large\textbf{#1}\normalsize}
\def\LRG#1{\LARGE\textbf{#1}\normalsize}

\def\headline#1{\hbox to \hsize{\hrulefill\quad\lower.3em\hbox{\lrg{#1}}\quad\hrulefill}\bigskip}

% begin a tabularx without indentation
\def\tabx#1{\noindent\begin{tabularx}{\textwidth}{#1}}

% column types for tables
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}


\begin{document}

% Remove page number
\clearpage
\thispagestyle{empty}


\tabx{L C R}
Phone: +7(904)856-51-29 & \LRG{Andrey Tonkikh}  & github profile: xosmig \\
Email: xosmig@gmail.com &                       & codeforces profile: xosmig \\
\end{tabularx}

\headline{Education}

\tabx{L C R}
\tbf{Saint Petersburg}    & BS in Computer Science & 2015-Present (2 year) \\
\tbf{Academic University} &                        & Overall GPA: 4.0 / 4.0 \\
                          &                        & Graduating May 2019 \\
\end{tabularx}

\headline{Programming languages}

\tabx{c L}
\tbf{Confident in:}       & C++, Rust \\
\tbf{Currently learning:} & Java, Haskell \\
\tbf{Small experience:}   & Python, Kotlin (I like this language and I hope I will start learning it soon) \\
\end{tabularx}
\smallskip

\headline{Technologies}

Git, Unix/Linux, Libgdx game framework (Java)
\smallskip

\headline{Projects}

\tabx{c L}
\tbf{Ghost Revenge} & A game for Android. Not a big game, just my first experience in game development
                      and my first release in Google play market. \\[5pt]
\tbf{Blackout}      & An open-source multiplayer 3D game for Android with good physics.
                      Not released yet. I'm currently working on it with a fellow student. \\[5pt]
\tbf{Hwformat}      & Pre-processor for latex which makes it easier for writing small mathematical texts.
                      Mainly for Russian language. Based on regular expressions. \\[5pt]
\tbf{xo\_os}        & An educational project in the university. Small x86-64 OS-kernel written in Rust. \\[5pt]
\end{tabularx}
\smallskip

\headline{Open source experience}

\noindent
I have several merged pull requests to Rust's standard collections library:
\medskip

\tabx{l L}
\tbf{std::BinaryHeap}   & \ttt{append} method (merge two binary heaps in optimal time).
                          Wasn't really hard. Just a first experience \\[5pt]
\tbf{std::BTreeMap} and & \ttt{append} method (merge two BTrees in optimal time). And \ttt{split\_off} \\
\tbf{std::BTreeSet}     & method. Both are in a stable release now. TODO: quantify your work. \\[5pt]
\end{tabularx}
\smallskip

\headline{Other experience}

\tabx{l L}
Programming & In a high school I was into programming contests and was awarded in some \\
contests    & important russian programming olympiads like "All-Russian Olympiad of School Students in Informatics"
              and "Open Programming Olympiad". But now I prefer to invest my time in
              development of engineering skills. \\[5pt]
Teaching    & I like to teach and I was a teacher for a month in "Summer Informatics School".
              This is a summer school for children who want to learn more
              about programming and algorithms than in a common school. \\[5pt]
Altai CTF   & My team was awarded in "Altai CTF" -- an information security competition for students
              (Actually, we was in school yet unlike most of our competitors). \\[5pt]
\end{tabularx}

% Also I was awarded in some mathematical olympiads.

\end{document}
